Changes From Preregistration

### 2020-04-20 analyses.Rmd
- initialized webpage
- updated feedback - updated website

---
title: "How Do Like and Dislike Buttons Affect Communication?"
shorttitle : "Analyses"
output: 
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    keep_md: true
---

```{r setup, include=F}
knitr::opts_chunk$set(
  cache=T, comment=NA, warning=F, echo=F, error=F, 
  message=F, prompt=F, tidy=T, fig.height=4
  )
options(digits = 3, width = 120)
```

```{r r-setup, include=F}
# define packages
packages <- c("cowplot", "devtools", "faoutlier", "GGally", "gganimate",
              "kableExtra", "knitr", "lavaan", "magrittr", "MVN", "psych", "pwr", 
              "quanteda", "semTools", "tidyverse")

# install packages # uncomment lines to install packages
# devtools::install_github("tdienlin/td@v.0.0.2.3")
# lapply(packages, install.packages, character.only = T, quietly = TRUE)

# load packages
lapply(packages, library, character.only = TRUE, quietly = TRUE)
library(td)
```

```{r Data-Wrangling, include=F}
# load data
# please note that in a prior step several different data sets were merged using information such as case_taken or IP-addresses. To guarantee the privacy of the participants, these data were deleted after merging.
d_raw <- read_csv("data/data_raw.csv")

@@

    # take logarithm
    posts_log = log1p(.$post_count),
    time_log = log1p(.$time_read), 
    posts_read_count_log = log1p(.$posts_read_count),
    words_log = log1p(.$words),
    self_dis_log = log1p(self_dis)
  )
```

```{r include=F}
# sample descriptives t1
n_t1 <- nrow(d)
age_t1_m <- mean(d$age, na.rm = TRUE)
male_t1_m <- mean(d$male, na.rm = TRUE)
college_t1_m <- table(d$edu)[3] / n_t1

@@

# save data file with all participants to compare results
d_all <- d

var_names_breaks <- c("Privacy\nconcerns", 
                      "General\ngratifications", 
                      "Specific\ngratifications",
                      "Privacy\ndeliberation", 
                      "Self-\nefficacy", 
                      "General\ntrust", 
                      "Specific\ntrust",
                      "Self-\ndisclosure")
```

@@

@@

We first inspected the data manually for cases with obvious response patterns. The following cases show extreme response patterns (alongside fast response times), and were hence removed.

@@

```{r}
name <- "pricon"
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

@@

factor_val_tab <- rbind(pricon_factor_val,
                        grats_general_factor_val,
                        grats_specific_factor_val,
                        pridel_factor_val,
                        selfeff_factor_val,
                        trust_gen_factor_val,
                        trust_spec_factor_val) %$%
  cbind(des[-8, ], .) %>%
  set_rownames(var_names[-8]) %T>%
  print()
```

@@

```{r zds, fig.height=8, fig.width=8}
fig_fs_cor <- ggpairs(
  select(d_fs, -version),
  upper = list(continuous = "cor"),
  lower = list(continuous = wrap(td::scat_plot, coords = c(1, 7, 0, 7)))) +
  theme_bw()
print(fig_fs_cor)
```

@@

```{r pwr-criteria, include=F}
z_crit <- 1.96
alpha <- .05
power_desired <- .95
r_sesoi <- .10
```

@@

```{r pwr-samplesize}
pwr.r.test(r = r_sesoi, sig.level = alpha, power = power_desired, alternative = "greater") %T>%
  print %$% 
  n %>% 
  round(0) ->
  n_desired
```

@@

```{r pwr-achieved}
pwr.r.test(n = n_final, r = r_sesoi, sig.level = alpha, alternative = "greater") %T>%
  print %$% 
  power %>% 
  round(2) ->
  power_achieved
```

@@

```{r pwr-sensitivity}
pwr.r.test(n = n_final, power = power_desired, sig.level = alpha, alternative = "greater") %T>%
  print %$% 
  r %>% 
  round(2) ->
  r_sensitive
```

@@

```{r eval=F}
cooks_dis <- gCD(d, model_baseline)
plot(cooks_dis)
```

@@

```{r eval=F}
infl_cases <- invisible(rownames(print(cooks_dis)))
```

@@

```{r eval=F}
infl_cases_tokens <- d[infl_cases, "case_token"] %>% as_vector()
d %>% 
  filter(case_token %in% infl_cases_tokens) %>% 
  select(case_token, GR01_01:SE01_06, topics_entered:reactions, -SO01_01, TIME_SUM_t1, TIME_SUM_t2) %>% 
  kable() %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
```

@@

```{r}
fig_fs_m <- ggplot(
  gather(d_fs, variable, value, -version) %>% 
    mutate(variable = factor(variable, levels = var_names_breaks)),
  aes(x = version, y = value, fill = version)) +
  stat_summary(fun.y = mean, geom = "bar") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .75) +
  facet_wrap(~ variable, nrow = 2) + 
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        plot.title = element_text(hjust = .5),
        panel.spacing = unit(.9, "lines"),
        text = element_text(size = 12),
        legend.position="bottom",
        legend.title = element_blank()) +
  scale_fill_brewer(palette="Greys")
fig_fs_m
```

@@

In what follows, we also report explicit statistical tests of the differences between the conditions using contrasts. However, please note that several models did not converge. This is likely because the models remain complex, while the sample size significantly decreases (i.e., only 2/3 of prior models).

@@

>>>>

---
title: "Analyses"
output: 
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
---

```{r setup, include=F}
knitr::opts_chunk$set(
  cache=T, comment=NA, warning=F, echo=T, error=F, 
  message=F, prompt=F, tidy=T, fig.height=4
  )
options(digits = 3, width = 120)
```

In what follows, you can find the analyses for the results we report in the paper. To see the underlying code, click on the button "code".

# Setup

We first load the packages; load and wrangle data; and extract sample characteristics and descriptives.

```{r results='hide'}
# install github packages
# devtools::install_github("tdienlin/td@v.0.0.2.3")  # uncomment to install

# define packages
packages <- c("cowplot", "devtools", "faoutlier", "GGally", "gganimate",
              "kableExtra", "knitr", "lavaan", "magrittr", "MVN", "psych", "pwr", 
              "quanteda", "semTools", "tidyverse", "td")

# load packages
lapply(packages, library, character.only = TRUE, quietly = TRUE)

# load data
# please note that in a prior step several different data sets were merged using information such as case_taken or IP-addresses. To guarantee the privacy of the participants, these data were deleted after merging.
d_raw <- read_csv("data/data_raw.csv")

@@

    # take logarithm
    posts_log = log1p(.$post_count),
    time_log = log1p(.$time_read), 
    posts_read_count_log = log1p(.$posts_read_count),
    words_log = log1p(.$words),
    self_dis_log = log1p(self_dis)
  )

var_names_breaks <- c("Privacy\nconcerns", 
                      "General\ngratifications", 
                      "Specific\ngratifications",
                      "Privacy\ndeliberation", 
                      "Self-\nefficacy", 
                      "General\ntrust", 
                      "Specific\ntrust",
                      "Self-\ndisclosure")

# Extract sample characteristics and descriptives.
# sample descriptives t1
n_t1 <- nrow(d)
age_t1_m <- mean(d$age, na.rm = TRUE)
male_t1_m <- mean(d$male, na.rm = TRUE)
college_t1_m <- table(d$edu)[3] / n_t1

@@

# save data file with all participants to compare results
d_all <- d
```

@@

We filtered participants who answered the questionnaire in less than three minutes, which we considered to be unreasonably fast.

@@

We inspected the data manually for cases with obvious response patterns. The following cases show extreme response patterns (alongside fast response times), and were hence removed.

@@

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

Updated version shows good fit.

@@

factor_val_tab <- rbind(pricon_factor_val,
                        grats_general_factor_val,
                        grats_specific_factor_val,
                        pridel_factor_val,
                        selfeff_factor_val,
                        trust_gen_factor_val,
                        trust_spec_factor_val) %$%
  cbind(des[-8, ], .) %>%
  set_rownames(var_names[-8])

factor_val_tab %>% 
  kable() %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
```

@@

```{r fig.height=8, fig.width=8}
fig_fs_cor <- ggpairs(
  select(d_fs, -version),
  upper = list(continuous = "cor"),
  lower = list(continuous = wrap(td::scat_plot, coords = c(1, 7, 0, 7)))) +
  theme_bw()
print(fig_fs_cor)
```

@@

```{r include=F}
# define pwr-criteria
z_crit <- 1.96
alpha <- .05
power_desired <- .95
r_sesoi <- .10
```

@@

```{r}
# estimate pwr-samplesize
pwr.r.test(r = r_sesoi, sig.level = alpha, power = power_desired, alternative = "greater") %T>%
  print %$% 
  n %>% 
  round(0) ->
  n_desired
```

@@

```{r}
# compute pwr-achieved
pwr.r.test(n = n_final, r = r_sesoi, sig.level = alpha, alternative = "greater") %T>%
  print %$% 
  power %>% 
  round(2) ->
  power_achieved
```

@@

```{r}
# estimate pwr-sensitivity
pwr.r.test(n = n_final, power = power_desired, sig.level = alpha, alternative = "greater") %T>%
  print %$% 
  r %>% 
  round(2) ->
  r_sensitive
```

@@

```{r eval=T}
cooks_dis <- gCD(d, model_baseline)
plot(cooks_dis)
```

@@

```{r eval=T}
infl_cases <- invisible(rownames(print(cooks_dis)))
```

@@

```{r eval=T}
infl_cases_tokens <- d[infl_cases, "case_token"] %>% as_vector()
d %>% 
  filter(case_token %in% infl_cases_tokens) %>% 
  select(case_token, GR01_01:SE01_06, topics_entered:reactions, -SO01_01, TIME_SUM_t1, TIME_SUM_t2) %>% 
  kable() %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
```

@@

```{r}
fig_fs_m <- ggplot(
  gather(d_fs, variable, value, -version) %>% 
    mutate(variable = factor(variable, levels = var_names_breaks)),
  aes(x = version, y = value, fill = version)) +
  stat_summary(fun.y = mean, geom = "bar") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .75) +
  facet_wrap(~ variable, nrow = 2) + 
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        plot.title = element_text(hjust = .5),
        panel.spacing = unit(.9, "lines"),
        text = element_text(size = 12),
        legend.position="bottom",
        legend.title = element_blank()) +
  coord_cartesian(ylim = c(0, 7)) +
  scale_fill_brewer(palette="Greys")
fig_fs_m
```

@@

In what follows, we also report explicit statistical tests of the differences between the conditions using contrasts.

However, please note that several models did not converge. This is likely because the models remain complex, while the sample size significantly decreases (i.e., only 2/3 of prior models).

For these models, we report less complex versions using factors scores, which converge successfully.

@@

Now converges sucessfully.

### 2020-04-20 index.Rmd
- updated feedback - updated website

Hello world.

>>>>

On this website, you can find the companion material for the paper _How Do Like and Dislike Buttons Affect Communication? A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment_.

You can either read the paper [online](manuscript.html) or download it as [pdf](manuscript.pdf). You can also find the detailed code and summaries of the [analyses](analyses.html) that were reported in the paper, as well as [additional analyses](analyses_additional.html) not reported in the paper.

This website is produced directly from the project's [github repository](https://github.com/tdienlin/privacy_calc_exp). You can download the material and the data, file an issue, or submit a pull request.

### 2020-04-20 manuscript.RmD
- updated feedback - updated website

---
title             : "How Do Like and Dislike Buttons Affect Communication? A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment"
shorttitle        : "Popularity cues and the privacy calculus"
author:            
  - name          : "Dienlin, Tobias"
    email         : "tobias.dienlin@uni-hohenheim.de"
    affiliation   : "1"
    corresponding : yes
    address       : "University of Hohenheim, Department of Media Psychology (540F), 70599 Stuttgart, Germany"
  - name          : "Braeunlich, Katharina"
    email         : "braeunlich@uni-koblenz.de"
    affiliation   : "2"
  - name          : "Trepte, Sabine"
    email         : "sabine.trepte@uni-hohenheim.de"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "University of Hohenheim"
  - id            : "2"
    institution   : "University of Koblenz-Landau"
author_note: |
  All authors contributed extensively to the work presented in this paper. TD, KB, & ST designed the study; KB & TD designed the online website; TD & KB administered the data collection and importation; TD wrote the code, ran the models, and analyzed the output data; TD wrote the manuscript and ST provided comments; ST supervised the project. 
  The authors declare no competing interests.

@@

  This manuscript features online supplementary material, which includes the data, code, additional analyses, and a reproducible version of the manuscript (https://osf.io/hcqat/?view_only=5db35868738d40609b11e58cc343a9b0).
abstract: |
    According to the privacy calculus, both privacy concerns and expected gratifications explain self-disclosure online. So far, however, most findings were based on self-reports, and little is known about whether the privacy calculus can be used to explain observations of actual behavior. Likewise, we still know little as to whether the privacy calculus can be influenced by the design of online websites, including for example popularity cues such as like and dislike buttons. To answer these questions, we ran a preregistered one-week field experiment. Participants were randomly distributed to three different websites, on which they discussed a current political topic. The final sample consisted of `r knitr::load_cache(label = "load-data", object = "n_matched")` participants. Although the originally preregistered model could not be confirmed, the results showed that a considerable share of actual self-disclosure could be explained by privacy concerns, gratifications, privacy deliberation, trust, and self-efficacy. The impact of the popularity cues on self-disclosure and the privacy calculus was negligible. In conclusion, the results suggest that privacy concerns and expected benefits are relevant when it comes to understanding self-disclosure, which together provides further evidence against the privacy paradox.
keywords          : "privacy calculus, self-disclosure, popularity cues, field experiment, structural equation modeling, preregistration"
bibliography      : 
  - [bibliography/r-references.bib]
  - [bibliography/references.bib]
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
wordcount         : "`r wordcountaddin::word_count('manuscript/manuscript.Rmd')`"
draft             : no
documentclass     : "apa6"
classoption       : "man"
# to compile as pdf
# (a) move file "_site.yml" to folder "tmp"
# (b) uncomment the following lines
# output            : papaja::apa6_pdf
# header-includes:
#   - \setlength{\parskip}{0em}
#   - \raggedbottom
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
---

```{r include=F}
knitr::opts_chunk$set(cache=F, echo=F)
```

```{r setup, include=F}
# load packages
pcks <- c("devtools", "jpeg", "knitr", "lavaan", "magrittr", "papaja", "png", "pwr", "semTools", "tidyverse")
invisible(lapply(pcks, library, character.only = TRUE))
# install_github("tdienlin/td@v.0.0.2.3")
library(td)

@@

Understanding why people disclose personal information online remains a critical question for both society and research. 
Originally, it was claimed that self-disclosure is mostly erratic, and that self-disclosure cannot be predicted by assessing people's personal beliefs, concerns, or standpoints. 
Most prominently, the privacy paradox stated that people self-disclose vast amounts of personal information online *despite* having substantial concerns about their privacy [@barnesPrivacyParadoxSocial2006; @taddickenUsesPrivacyOnline2011].

@@

Self-disclosure is a primary means of regulating privacy [e.g., @masurSituationalPrivacySelfdisclosure2018].
It is our key variable of interest.
There are two different understandings of self-disclosure in the literature: 
The first defines self-disclosure as _deliberate_ acts of sharing truthful information about the self with others [@jourardTransparentSelf1964]. 
The second considers _all_ acts of sharing information---be they active or passive, deliberate or unwitting---as self-disclosure, because each piece of information allows for meaningful inferences about a person [@watzlawickPragmaticsHumanCommunication2011]. 
In this paper we follow the latter approach, not least because the recent years have illustrated how easy it is to derive personal insights simply by analyzing exchanged communication [@kosinskiPrivateTraitsAttributes2013]. 
Moreover, independent from which position one adopts, it is possible to differentiate the content of self-disclosure into three different dimensions: breadth (i.e., number of topics covered), depth (i.e., intimacy of topics covered), and length (i.e., quantity of disclosure) [@omarzuDisclosureDecisionModel2000]. 
In this study we mainly focus on communication quantity, as we consider communication quantity to be a necessary precondition and hence valid proxy for self-disclosure.

@@

Several attempts have already been made to expand the privacy calculus [@dinevExtendedPrivacyCalculus2006], introducing additional variables such as self-efficacy or trust. 
Self-efficacy in the context of the privacy calculus captures whether people believe in their own capability to implement particular privacy behaviors in the future [@dienlinExtendedPrivacyCalculus2016].
These privacy behaviors refer to either self-_disclosure_ (e.g., publishing a blog post) or self-_withdrawal_ (e.g., deleting inappropriate content).
People who report more privacy self-efficacy also engage in more self-withdrawal  [@chenRevisitingPrivacyParadox2018].
In light of our focus on active communication, in this study we investigate the influence of self-_disclosure_ self-efficacy.

@@

Trust can be conceptualized in two different ways [@gefenTrustTAMOnline2003]: 
It either captures "_specific_ beliefs dealing primarily with the integrity, benevolence, and ability of another party" [@gefenTrustTAMOnline2003, p. 55, emphasis added] or a "_general_ belief that another party can be trusted" [@gefenTrustTAMOnline2003, p.55, emphasis added]. 
Whereas specific trust focuses on the causes of trust, general trust emphasized the experience of trust.
@gefenTrustTAMOnline2003 prioritize specific trust (p. 60). 
In the online context, it is also important to differentiate among several _targets_ of trust [@sollnerWhyDifferentTrust2016]. 
Potential targets include (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users [@sollnerWhyDifferentTrust2016]. 
Trust plays a key role in online communication [@metzgerPrivacyTrustDisclosure2004]. 
For example, people who put more trust in the providers of networks also disclose more personal information [@liEmpiricalStudiesOnline2011].

@@

The online supplementary material (OSM) of this study includes the data, research materials, analyses scripts, and a reproducible version of this manuscript (see https://osf.io/hcqat/?view_only=5db35868738d40609b11e58cc343a9b0).
We preregistered the study using the registration form _OSF Prereg_, which includes the hypotheses, sample size, research materials, analyses, and exclusion criteria (see https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859). 
We needed to change our pre-defined plan in some cases. 
For a full account of all changes, see OSM. 
New analyses that were not preregistered appear in the section on exploratory analyses.

@@

We collaborated with a professional panel agency to recruit participants. 
As incentive, participants were awarded digital points, which they could use to get special offers from other companies. 
Participants were above the age of 18 and lived in Germany. 
In a first step, the agency sent its panel members an invitation to participate in the study (_invitation_). 
In this invitation, panel members were asked to participate in a study analyzing the current threat posed by terrorist attacks in Germany.[^1] 
Members who decided to take part were subsequently sent the first questionnaire (_T1_), in which we asked about their sociodemographics, provided more details about the study, and included a registration link for the website. 
Afterward, participants were randomly assigned to one of the three websites. 
After registration was completed, participants could discuss the topic of the terrorism threat in Germany over the course of one week (_field_). 
Subsequently, participants received a follow-up questionnaire in which the self-reported measures were collected (_T2_). 
Measures were collected after and not before the field phase in order not to prime participants or reveal our primary research interest.

@@

Self-disclosure was calculated by taking the log scale of the number of words each participant wrote in a comment, to which we added the number of likes and dislikes, which were multiplied by two. 
The number of likes and dislikes were multiplied by two because, rudimentarily, like buttons abbreviate the sentence “I like” and dislike buttons “I dislike”.
The sum of words and likes/dislikes was log-scaled because the relative amount of self-disclosure diminishes the more a person has already said.

@@

```{r popularitycues, fig.cap="Overview of the variables for the three websites. Control: Website without buttons. Like: Website with like buttons. Like \\& Dislike: Website with like and dislike buttons.", out.width = "\\textwidth", fig.pos = "!h"}
# knitr::include_graphics("figures/results/fig_pop.pdf")
print(fig_fs_m)
```

>>>>

---
title             : "How Do Like and Dislike Buttons Affect Communication? A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment"
shorttitle        : "Popularity cues and the privacy calculus"
author:            
  - name          : "Dienlin, Tobias"
    email         : "tobias.dienlin@uni-hohenheim.de"
    affiliation   : "1"
    corresponding : yes
    address       : "University of Hohenheim, Department of Media Psychology (540F), 70599 Stuttgart, Germany"
  - name          : "Braeunlich, Katharina"
    email         : "braeunlich@uni-koblenz.de"
    affiliation   : "2"
  - name          : "Trepte, Sabine"
    email         : "sabine.trepte@uni-hohenheim.de"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "University of Hohenheim"
  - id            : "2"
    institution   : "University of Koblenz-Landau"
author_note: |
    All authors contributed extensively to the work presented in this paper. TD, KB, & ST designed the study; KB & TD designed the online website; TD & KB administered the data collection and importation; TD wrote the code, ran the models, and analyzed the output data; TD wrote the manuscript, ST provided comments; ST supervised the project. The authors declare no competing interests.

@@

    This manuscript features online supplementary material, which includes the data, code, additional analyses, and a reproducible version of the manuscript (https://tdienlin.github.io/privacy_calc_exp).
abstract: |
    According to the privacy calculus, both privacy concerns and expected gratifications explain self-disclosure online. So far, however, most findings were based on self-reports, and little is known about whether the privacy calculus can be used to explain observations of actual behavior. Likewise, we still know little as to whether the privacy calculus can be influenced by the design of online websites, including for example popularity cues such as like and dislike buttons. To answer these questions, we ran a preregistered one-week field experiment. Participants were randomly distributed to three different websites, on which they discussed a current political topic. The final sample consisted of `r knitr::load_cache(label = "load-data", object = "n_matched")` participants. Although the originally preregistered model could not be confirmed, the results showed that a considerable share of actual self-disclosure could be explained by privacy concerns, gratifications, privacy deliberation, trust, and self-efficacy. The impact of the popularity cues on self-disclosure and the privacy calculus was negligible. In conclusion, the results suggest that privacy concerns and expected benefits are relevant when it comes to understanding self-disclosure, which together provides further evidence against the privacy paradox.
keywords          : "privacy calculus, self-disclosure, popularity cues, field experiment, structural equation modeling, preregistration"
bibliography      : 
  - [bibliography/r-references.bib]
  - [bibliography/references.bib]
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
draft             : no
documentclass     : "apa6"
classoption       : "man"
# to compile as pdf
# (a) move file "_site.yml" to folder "tmp"
# (b) uncomment the following lines
# output            : papaja::apa6_pdf
# header-includes:
#   - \setlength{\parskip}{0em}
#   - \raggedbottom
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
---

```{r include=F}
knitr::opts_chunk$set(cache=F, echo=F, warning=F, message=F)
```

```{r setup, include=F}
# install github packages
# devtools::install_github("tdienlin/td@v.0.0.2.3")

# load packages
pcks <- c("devtools", "jpeg", "knitr", "lavaan", "magrittr", "papaja", "png", "pwr", "semTools", "td", "tidyverse")
invisible(lapply(pcks, library, character.only = TRUE))

@@

Understanding why people disclose personal information online remains a critical question for both society and research. 
Originally, it was claimed that self-disclosure is erratic and that it cannot be predicted people's personal beliefs, concerns, or standpoints. 
Most prominently, the privacy paradox stated that people self-disclose vast amounts of personal information online *despite* having substantial concerns about their privacy [@barnesPrivacyParadoxSocial2006; @taddickenUsesPrivacyOnline2011].

@@

Self-disclosure is a primary means of regulating privacy [e.g., @masurSituationalPrivacySelfdisclosure2018].
It is our key variable of interest.
There are two different understandings of self-disclosure in the literature: 
The first defines self-disclosure as _deliberate_ acts of sharing truthful information about the self with others [@jourardTransparentSelf1964]. 
The second considers _all_ acts of sharing information---be they active or passive, deliberate or unwitting---as self-disclosure, because each piece of information allows for meaningful inferences about a person [@watzlawickPragmaticsHumanCommunication2011]. 
In this paper we follow the latter approach, not least because the recent years have illustrated how easy it is to derive personal insights simply by analyzing exchanged communication [@kosinskiPrivateTraitsAttributes2013]. 
Moreover, independent from which position one adopts, it is possible to differentiate the content of self-disclosure into three different dimensions: breadth (i.e., number of topics covered), depth (i.e., intimacy of topics covered), and length (i.e., quantity of disclosure) [@omarzuDisclosureDecisionModel2000]. 
In this study we mainly focus on communication quantity as proxy for self-disclosure.
The relation between communication quantity and self-disclosure is not linear. 
Impressions are formed quickly, and the more we have already expressed about ourselves the harder it becomes to self-disclose novel information.

@@

Several attempts have already been made to expand the privacy calculus, introducing additional variables such as self-efficacy or trust [@dinevExtendedPrivacyCalculus2006]. 
Self-efficacy in the context of the privacy calculus captures whether people believe in their own capability to implement particular privacy behaviors in the future [@dienlinExtendedPrivacyCalculus2016].
These privacy behaviors refer to either self-_disclosure_ (e.g., publishing a blog post) or self-_withdrawal_ (e.g., deleting inappropriate content).
People who report more privacy self-efficacy also engage in more self-withdrawal  [@chenRevisitingPrivacyParadox2018].
In light of our focus on active communication, in this study we investigate the influence of self-_disclosure_ self-efficacy.

@@

The next variable, trust, can be conceptualized in two different ways [@gefenTrustTAMOnline2003]: 
It either captures "_specific_ beliefs dealing primarily with the integrity, benevolence, and ability of another party" [@gefenTrustTAMOnline2003, p. 55, emphasis added] or a "_general_ belief that another party can be trusted" [@gefenTrustTAMOnline2003, p.55, emphasis added]. 
Whereas specific trust focuses on the causes of trust, general trust emphasized the experience of trust.
@gefenTrustTAMOnline2003 prioritize specific trust (p. 60). 
In the online context, it is also important to differentiate among several _targets_ of trust [@sollnerWhyDifferentTrust2016]. 
Potential targets include (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users [@sollnerWhyDifferentTrust2016]. 
Trust plays a key role in online communication [@metzgerPrivacyTrustDisclosure2004]. 
For example, people who put more trust in the providers of networks also disclose more personal information [@liEmpiricalStudiesOnline2011].

@@

The online supplementary material (OSM) of this study includes the data, research materials, analyses scripts, and a reproducible version of this manuscript, which can be found on the manuscript's online companion website (https://tdienlin.github.io/privacy_calc_exp).
We preregistered the study using the registration form _OSF Prereg_, which includes the hypotheses, sample size, research materials, analyses, and exclusion criteria (see https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859). 
We needed to change our pre-defined plan in some cases. 
For a full account of all changes, see OSM. 
New analyses that were not preregistered appear in the section on exploratory analyses.

@@

We collaborated with a professional panel agency to recruit participants. 
As incentive, participants were awarded digital points, which they could use to get special offers from other companies. 
Participants were above the age of 18 and lived in Germany. 
In a first step, the agency sent its panel members an invitation to participate in the study (_invitation_). 
In this invitation, panel members were asked to participate in a study analyzing the current threat posed by terrorist attacks in Germany.[^1] 
Members who decided to take part were subsequently sent the first questionnaire (_T1_), in which we asked about their sociodemographics, provided more details about the study, and included a registration link for the website. 
Afterward, participants were randomly assigned to one of the three websites. 
After registration was completed, participants were invited (but not obliged) to discuss the topic of the terrorism threat in Germany over the course of one week (_field_). 
Subsequently, participants received a follow-up questionnaire in which the self-reported measures were collected (_T2_). 
Measures were collected after and not before the field phase in order not to prime participants or reveal our primary research interest.

@@

Self-disclosure was calculated by taking the log scale of the number of words each participant wrote in a comment, to which we added the number of likes and dislikes, which were multiplied by two. 
The number of likes and dislikes were multiplied by two because, rudimentarily, like buttons abbreviate the sentence “I like” and dislike buttons “I dislike”.
The sum of words and likes/dislikes was log-scaled because the relative amount of self-disclosure diminishes the more a person has already expressed.

@@

```{r popularitycues, fig.cap="Overview of the model-predicted values for each variable, separated for the three websites. Control: Website without buttons. Like: Website with like buttons. Like \\& Dislike: Website with like and dislike buttons.", out.width = "\\textwidth", fig.pos = "!h"}
print(fig_fs_m)
```
